Unit tests

### 2018-03-09 Tests.Rmd
added tests for OurBiCopSelect

>>>>

# Tests to model selection tool

We here test the `OurBiCopSelect` function with simulated data.

Data are simulated from a Clayton copula with parameter 8:
```{r get_data_test, echo=T}
source("getcopula.R")
source("OurBiCopSelect.R")
set.seed(101)
cop<-claytonCopula(8,2)
d<-rCopula(1000,cop)
v<-getcopula(d=d,rankon=F,ploton=T) #with real data, rankon should be T
```

Now apply the function:
```{r bivmodselect_test, echo=F, cache=T, cache.extra=list(d,mtime("OurBiCopSelect.R"))}
families<-c(1,3,4,5,13)
BivMS_res_test<-OurBiCopSelect(d[,1],d[,2],families=families,gofnormal=TRUE,status=TRUE)
```

Independence should be rejected (low $p$ value):
```{r echo=T}
BivMS_res_test$IndepTestRes
```

Model selection should support the actual model (Clayton):
```{r echo=T}
BivMS_res_test$InfCritRes
```

The actual model (Clayton) should not be rejected:
```{r echo=T}
BivMS_res_test$GofRes_CvM
BivMS_res_test$GofRes_KS
```

Look at goodness-of-fit results for the normal copulas:
```{r echo=T}
BivMS_res_test$GofRes_Normal_CvM
BivMS_res_test$GofRes_Normal_KS
```
